Homework

### 2016-06-29 Macro Impacts.tex
More Stuff
Butts
Vector modes
some more to come

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics, MnSymbol,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

@@

@@

>>>>

\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathtools, calrsfs, tensor, physics,tikz-cd}
\usepackage[mathscr]{euscript}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{enumitem}
\setlist[description]{font=\normalfont}

@@

\section{Scalar Modes}

@@

\pagebreak
\section{Vector Modes}
The following is the equation of motion for the vector potential $a$ without body force:
\mu\nabla^2a-\rho\ddot a=\mu\nabla(\nabla\cdot a)-\mu\nabla\times(\nabla\times a)-\rho\ddot a=0\,,
where the leftmost term is the vector laplacian. This gives us three wave equations for the three components of $a$. The constraint equation takes the form
\sigma_{ij}&=\lambda\delta_{ij}\nabla\cdot \nabla\times a+\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
&=\mu(\partial_j (\nabla\times a)_i+\partial_i (\nabla\times a)_j)\,,\\
&=\mu\mat{ccc}{2\partial_x(\partial_ya_z-\partial_za_y)&(\partial_y^2-\partial_x^2)a_z+\partial_z(\partial_x a_x-\partial_y a_y)&(\partial_x^2-\partial_z^2)a_y+\partial_y(\partial_z a_z-\partial_x a_x)\\
&2\partial_y(\partial_z a_x-\partial_x a_z)&(\partial_z^2-\partial_y^2)a_x+\partial_x(\partial_ya_y-\partial_za_z)\\
&&2\partial_z(\partial_xa_y-\partial_ya_x)}\,.
